SeedLing: Building and using a seed corpus \\ for the Human Language Project

### 2014-04-28 docs/computEL-final/paper.tex
Corrections, mainly in evaluation.

\author{Guy Emerson, Liling Tan, Susanne Fertmann, Alexis Palmer and Michaela Regneri \\
Universität des Saarlandes \\
66123 Saarbrücken, Germany \\
{\tt \{emerson, liling, susfert, apalmer, regneri\}} \\
{\tt @coli.uni-saarland.de} \\
}
\date{}

>>>>

\author{Guy Emerson, Liling Tan, \\ \textbf{Susanne Fertmann, Alexis Palmer} \\
Universität des Saarlandes \\
66123 Saarbrücken, Germany \\
{\tt \{emerson, liling, susfert,} \\ {\tt apalmer\}@coli.uni-saarland.de} \\\And
Michaela Regneri \\
IT-Department \\
SPIEGEL-Verlag \\
Hamburg, Germany \\
{\tt michaela\_regneri@spiegel.de}}

\date{}
